Reading Notes

### 2020-08-27 2pd.tex
deleting comments that have been resolved

In order to use coarse grain models to predict charge transport, we need a way to translate from the coarse to the atomistic morphology.
%% HELP transition
MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse-grained morphology.
%% MorphCT has some built in backmapping tools which use an xml file, but  (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
%%<making morphct more modular to allow it to be used in a workflow not cli>

@@

%%<how do I relate this to what I want to do??>
I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel\cite{mbuild, foyer, signac, fresnel}.
These contributions have given me ample opportunity to excercise best software development practices like writing good documentation, using version control, writing unit tests, employing CI, using a fork \& pull workflow, etc.
This experience will help me to be more efficient in my future work.
I've also gained valuable experience as working as part of a team.
As I plan to integrate my future work with existing projects, good collaborative skills will be necessary.

%% experience teaching and creating material for people to learn
I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}
%%- started development on UFF repo for foyer.
%%This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
%%<atom typing is a pain and doing it manually is bad cite foyer paper>

@@

We propose a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
This makes it a good candidate for specifying a coarse-grain mapping scheme.
The open-source package, Open Babel, allows for a SMILES string to be converted to a chemical structure and vice versa\cite{openbabel, OBoyle2011}.
SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
This pattern matching is also implemented in the Open Babel package.
If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered\cite{grits}.
%% another application?
This mapping scheme could even be used to make the mapping process easier for established coarse-grained models.
It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
This could make parameterizing new compounds for an existing method more foolproof.

@@

%% make better opvs
%% need to get a morphology on relevant lengthscale
%% many different chemistries
%% need a model that get a cg model from a chemistry

@@

%% Objectives are like steps along the way
%% objectives should be
% 1. goal of the step
% 2. how to do the step
% how doing this achieves the goal
%% how to coarse-grained reproducibly
\subsection*{Objective 1: Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
% mapping
% ff creation
% infrastructure: porting ff to engine
In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
This objective consists of three steps:
\begin{enumerate}
    \item {Create a tool that uses a mapping operator to go from atomistic to coarse-grained structure}
    \item {Use the mapped coarse-grained structure to parameterize a force field using MSIBI}
    \item {Develop the infrastructure to port this force field to a simulation engine}
\end{enumerate}
A minimum working example of this coarse-grained mapping tool has been completed\cite{grits}.
However, it will still need to be tested with many more compounds and mapping operators.
This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the Open Babel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
A minimum working example of an MSIBI tool has also been started; however, although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code\cite{msibi, Moore2014}.
The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
For this, we will make use of and build upon the simulation setup capabilities of mbuild.

@@

\textbf{Completion Critera:} 
Validation using diffraction or RDF of simulated morphologies composed of 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
%%\ej{Some number of predicted morphologies and/or some number of morphologies validated against experiments. }
% predict nanostructure of new opv blends TODO new objective?
% do math --- how long will it take me to graduate? how many sims can i do?

@@

Our lab has shown that we have the capability to compare our simulation results to experiment using hole mobilities from charge transport calculations\cite{Jones2017,Miller2018a} and grazing incedent X-ray scattering (GIXS) patterns\cite{Miller2018}.
GIXS calculations on our backmapped trajectories can be used to validate that our simulations result in the same morphology as experiment.
While charge transport calculations can be used to rate the efficacy of the active layer morphology.
Using our lab's charge transport package (MorphCT) on new chemistries, however, will require some work.
Many of the parameters and the definition of the chromophore are hard-coded for poly-3-hexylthiophene (P3HT).
Moving this package away from a command line interface will also be a goal of this work.
%%Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
%%<I need something in here about making morphct more user friendly and less hard-coded for p3ht.>
%%<adding in calculation of reorganization energy??> 
%%<or just ripping out the KMC bit and making it modular>

@@

%%<what's going to be hard?> 
Although minimum working examples have been developed for both the coarse-graining and backmapping packages, I still expect to struggle when mapping new compounds.
Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the sites matters) or chemically sensible (e.g., one SMILES string may contain another --- just as one chemical moeity may be composed of more submoeities). %%<this is a word?>)

>>>>

In order to use coarse grain models to predict charge transport, we need a way to translate from the coarse to the atomistic morphology.
%% HELP transition
MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse-grained morphology.

@@

I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel\cite{mbuild, foyer, signac, fresnel}.
These contributions have given me ample opportunity to excercise best software development practices like writing good documentation, using version control, writing unit tests, employing CI, using a fork \& pull workflow, etc.
This experience will help me to be more efficient in my future work.
I've also gained valuable experience as working as part of a team.
As I plan to integrate my future work with existing projects, good collaborative skills will be necessary.

I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}

@@

We propose a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
This makes it a good candidate for specifying a coarse-grain mapping scheme.
The open-source package, Open Babel, allows for a SMILES string to be converted to a chemical structure and vice versa\cite{openbabel, OBoyle2011}.
SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
This pattern matching is also implemented in the Open Babel package.
If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered\cite{grits}.
This mapping scheme could even be used to make the mapping process easier for established coarse-grained models.
It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
This could make parameterizing new compounds for an existing method more foolproof.

@@

@@

\subsection*{Objective 1: Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
This objective consists of three steps:
\begin{enumerate}
    \item {Create a tool that uses a mapping operator to go from atomistic to coarse-grained structure}
    \item {Use the mapped coarse-grained structure to parameterize a force field using MSIBI}
    \item {Develop the infrastructure to port this force field to a simulation engine}
\end{enumerate}
A minimum working example of this coarse-grained mapping tool has been completed\cite{grits}.
However, it will still need to be tested with many more compounds and mapping operators.
This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the Open Babel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
A minimum working example of an MSIBI tool has also been started; however, although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code\cite{msibi, Moore2014}.
The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
For this, we will make use of and build upon the simulation setup capabilities of mbuild.

@@

\textbf{Completion Critera:} 
Validation using diffraction or RDF of simulated morphologies composed of 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
%%\ej{Some number of predicted morphologies and/or some number of morphologies validated against experiments. }

@@

Our lab has shown that we have the capability to compare our simulation results to experiment using hole mobilities from charge transport calculations\cite{Jones2017,Miller2018a} and grazing incedent X-ray scattering (GIXS) patterns\cite{Miller2018}.
GIXS calculations on our backmapped trajectories can be used to validate that our simulations result in the same morphology as experiment.
While charge transport calculations can be used to rate the efficacy of the active layer morphology.
Using our lab's charge transport package (MorphCT) on new chemistries, however, will require some work.
Many of the parameters and the definition of the chromophore are hard-coded for poly-3-hexylthiophene (P3HT).
Moving this package away from a command line interface will also be a goal of this work.
%%Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
%%<adding in calculation of reorganization energy??> 
%%<or just ripping out the KMC bit and making it modular>

@@

Although minimum working examples have been developed for both the coarse-graining and backmapping packages, I still expect to struggle when mapping new compounds.
Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the sites matters) or chemically sensible (e.g., one SMILES string may contain another --- just as one chemical moeity may be composed of more submoeities). %%<this is a word?>)
